### 2010-06-26 paper/IIWAS2010/content/related_work.tex
updates from friday meeting

Question Answering (QA) is an old field and there has been a recent influx of QA work. The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.  Closed domain QA systems are those in which the possible meanings of the questions given are finite. We define closed corpus sytems as those in which the sources used to answer questions are finite.  QA systems that treat the web as a document collection is considered an open corpus system.  The morpheus system is considered an open corpus system.  It goes beyond current state of the art QA systems by examining deep web sources.

Several community QA systems have been developed, one of the most popular being Yahoo! Answers \cite{yahooanswers2008}.  These sites enlist a community of users to answer question posed by other users.  This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}. In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g. instant message, mobile phone).  This allows for a possibly faster answers to questions.  The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.

@@

\subsection{NLP Interfaces}

>>>>

Question Answering (QA) is an old field and there has been a recent influx of QA work. The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.  Closed domain QA systems are those in which the possible meanings of the questions given are finite. We define closed corpus sytems as those in which the sources used to answer questions are finite.  QA systems that treat the web as a document collection are open corpus systems.  The morpheus system is considered an open corpus system.  It goes beyond current state of the art QA systems by examining deep web sources.

Several community QA systems have been developed, one of the most popular being Yahoo! Answers \cite{yahooanswers2008}.  These sites enlist a community of users to answer question posed by other users.  This idea has evolved to invent socially integrated QA systems such as Aardvark \cite{vark2010}. In addition to having questions answered by users, Aardvark is able to contact potential question answerers through several media beyond webpages (e.g. instant messages, mobile phones).  This allows for possibly faster answers to questions.  The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.

@@

%\subsection{NLP Interfaces}
